### 2019-03-11 paper/sex_selection_spacing-ver2.tex
Add regional bootstrap tables
Add table with state names by region
Explain region creation

\FloatBarrier

@@

@@

\section{[Bootstrap Results by Region]}

@@

>>>>

@@

To examine the effect of differences in son preference, fertility, and use of sex 
selection on birth spacing, I divide India into four broad regions based on degree of 
son preference and initial fertility levels as in  \citet{retherford03b}, although 
expanded to include all states in the surveys.
Table \ref{tab:regions} shows the four regions and the states that they contain.%
\footnote{
The geographical names do not perfectly reflect the geography of India, and mainly
serves as mnemonic short-hands.
}
The state names are based on the states in existence when NFHS-1 was collected.
States that are formed later are allocated as closely as possible to the original state.

\input{../tables/desc_region.tex}

The West contains states with a high degree of son preference and use of sex selection.
The North consists of states that also have a strong son preference, but initially had
higher fertility and therefore lower likelihood of using sex selection.
The East states generally have only a moderate level of son preference.
Finally, the South contains states with traditionally low son preference and lower
fertility than the rest of India.

@@

@@

\section{Results by Region}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r1.tex}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r2.tex}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r3.tex}

\input{../tables/bootstrap_duration_avg_sex_ratio_high_r4.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r1.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r2.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r3.tex}

\input{../tables/bootstrap_duration_p25_p75_high_r4.tex}
